### 2022-08-08 msca-pf-part-b1.tex
add template for part b1

\documentclass[11pt,draftproposal]{msca-pf-2022}
% {{{ packages

% math
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{mathrsfs}
\usepackage{cases}

% pretty links
\usepackage{xparse}
\usepackage[hypertexnames=false,breaklinks=true]{hyperref}
\usepackage[nameinlink, noabbrev]{cleveref}
\usepackage[round]{natbib}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    citecolor=black,
    linkcolor=black
}

% better environments
\usepackage[shortlabels]{enumitem}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{subcaption}

% better typography
\usepackage[activate={true,nocompatibility}, % activate protrusion and font expansion
            final,              % enable microtype, use draft to disable
            tracking=true,
            kerning=true,       % optimise interactions between characters
            spacing=true,       % more uniform spacing between words
            factor=1100,        % more protrusion
            stretch=10,         % smaller values (default 20, 20) to avoid blurring
            shrink=10]{microtype}
\SetTracking{encoding={*}, shape=sc}{40}

% }}}

% {{{ formatting

% caption format
% NOTE: set format=plain to remove caption indentation
\captionsetup{
    format=hang
}

% }}}

% {{{ title

\title{Part B-1}
\author{}
\date{}

% }}}

\begin{document}

\maketitle

\section{Excellence}

\subsection{Quality and pertinence of the project's research and innovation objectives}

At a minimum, address the following aspects:

\begin{itemize}
    \item Describe the quality and pertinence of the R \& I objectives; are the
    objectives measurable and verifiable? Are they realistically achievable?

    \item Describe how your project goes beyond the state-of-the-art, and the
    extent to which the proposed work is ambitious.
\end{itemize}

\subsection{Soundness of the proposed methodology}

At a minimum, address the following aspects:

\begin{itemize}
    \item \emph{Overall methodology}: Describe and explain the overall methodology,
    including the concepts, models and assumptions that underpin your work.
    Explain how this will enable you to deliver your project’s objectives. Refer
    to any important challenges you may have identified in the chosen methodology
    and how you intend to overcome them.

    \item \emph{Integration of methods and disciplines to pursue the objectives}:
    Explain how expertise and methods from different disciplines will be brought
    together and integrated in pursuit of your objectives. If you consider that
    an inter-disciplinary\footnotemark{} approach is unnecessary in the
    context of the proposed work, please provide a justification.

    \footnotetext{Interdisciplinarity means the integration of information, data,
    techniques, tools, perspectives, concepts or theories from two or more
    scientific disciplines.}

    \item \emph{Gender dimension and other diversity aspects}: Describe how the
    gender dimension and other diversity aspects are taken into account in the
    project's research and innovation content. If you do not consider such a
    gender dimension to be relevant in your project, please provide a
    justification.
    \begin{itemize}
        \item Remember that that this question relates to the content of the
        planned research and innovation activities, and not to gender balance
        in the teams in charge of carrying out the project.

        \item  Sex, gender and diversity analysis refers to biological
        characteristics and social/cultural factors respectively. For guidance on
        methods of sex / gender analysis and the issues to be taken into account,
        please refer to
        \href{https://ec.europa.eu/info/news/gendered-innovations-2-2020-nov-24_en}{this page}.
    \end{itemize}

    \item \emph{Open science practices}: Describe how appropriate open science
    practices are implemented as an integral part of the proposed methodology.
    Show how the choice of practices and their implementation is adapted to the
    nature of your work in a way that will increase the chances of the project
    delivering on its objectives [e.g. up to 1/2 page, including research data
    management]. If you believe that none of these practices are appropriate for
    your project, please provide a justification here.

    \item \emph{Open science is an approach based on open cooperative work and systematic
    sharing of knowledge and tools as early and widely as possible in the process.
    Open science practices include early and open sharing of research (for example
    through pre-registration, registered reports, pre-prints, or crowd-sourcing);
    research output management; measures to ensure reproducibility of research
    outputs; providing open access to research outputs (such as publications,
    data, software, models, algorithms, and workflows); participation in open
    peer-review; and involving all relevant knowledge actors including citizens,
    civil society and end users in the co-creation of R\&I agendas and contents
    (such as citizen science).}

    \item \emph{Please note that this does not refer to outreach actions that may be
    planned as part of the communication, dissemination and exploitation activities.
    These aspects should instead be described below under ``Impact''.}

    \item \emph{Research data management and management of other research outputs}:
    Applicants generating/collecting data and/or other research outputs (except for
    publications) during the project must explain how the data will be managed
    in line with the FAIR principles (Findable, Accessible, Interoperable,
    Reusable).

    \item \emph{For guidance on open science practices and research data management,
    please refer to the relevant section of the \href{https://ec.europa.eu/info/funding-tenders/opportunities/docs/2021-2027/horizon/guidance/programme-guide_horizon_en.pdf}{HE Programme Guide}
    on the Funding \& Tenders Portal.}
\end{itemize}

\subsection{Quality of the supervision, training and of the two-way transfer of
knowledge between the researcher and the host}

At a minimum, address the following aspects:

\begin{itemize}
    \item Describe the qualifications and experience of the supervisor(s).
    Provide information regarding the supervisors' level of experience on the
    research topic proposed and their track record of work, including main
    international collaborations, as well as the level of experience in
    supervising/training, especially at advanced level (i.e. PhD and postdoctoral
    researchers).

    \item Planned training activities for the researcher (scientific aspects,
    management/organisation, horizontal and key transferrable skills...).

    \item For \emph{European Fellowships}: two-way transfer of knowledge between
    the researcher and host organisation.

    \item For \emph{Global Fellowships}: three-way transfer of knowledge between
    the researcher, host organisation, and associated partner for outgoing phase.

    \item Rationale and added-value of the non-academic placement (if applicable).
\end{itemize}

Employers and/or founders should ensure that a person is clearly identified to
whom researchers can refer for the performance of their professional duties, and
should inform the researchers accordingly.

Such arrangements should clearly define that the proposed supervisors are
sufficiently expert in supervising research, have the time, knowledge, experience,
expertise and commitment to be able to offer the postdoctoral researcher
appropriate support and provide for the necessary progress and review procedures,
as well as the necessary feedback mechanisms.

\textbf{Supervision} is one of the crucial elements of successful research. Guiding,
supporting, directing, advising and mentoring are key factors for a researcher
to pursue his/her career path. In this context, all MSCA-funded projects are
encouraged to follow the recommendations outlined in the
\href{https://data.europa.eu/doi/10.2766/508311}{MSCA Guidelines on Supervision}\footnotemark{}.

\footnotetext{While the MSCA Guidelines on Supervision are non-binding,
funded-projects are strongly encouraged to take them into account.}

\subsection{Quality and appropriateness of the researcher's professional
experience, competences and skills}

Discuss the quality and appropriateness of the researcher’s existing professional
experience in relation to the proposed research project.

\section{Impact}

\subsection{Credibility of the measures to enhance the career perspectives
and employability of the researcher and contribution to his/her skills
development}

At a minimum, address the following aspects:

\begin{itemize}
    \item \emph{Expected} skill development of the researcher.
    \item \emph{Expected} impact of the proposed research and training activities on
    the researcher's career perspectives inside and/or outside academia.
\end{itemize}

\subsection{Suitability and quality of the measures to maximise expected
outcomes and impacts, as set out in the dissemination and exploitation plan,
including communication activities}

At a minimum, address the following aspects:

\begin{itemize}
    \item \emph{Plan for the dissemination and exploitation activities, including
    communication activities}\footnotemark{}: Describe the planned measures to
    maximize the impact of your project by providing a first version of your ‘plan
    for the dissemination and exploitation including communication activities’.
    Describe the dissemination, exploitation measures that are planned, and the target
    group(s) addressed (e.g. scientific community, end users, financial actors,
    public at large). Regarding communication measures and public engagement
    strategy, the aim is to inform and reach out to society and show the activities
    performed, and the use and the benefits the project will have for citizens.
    Activities must be strategically planned, with clear objectives, start at the
    outset and continue through the lifetime of the project. The description of
    the communication activities needs to state the main messages as well as the
    tools and channels that will be used to reach out to each of the chosen target
    groups.

    \footnotetext{In case your proposal is selected for funding, a more detailed
    Dissemination and Exploitation plan will need to be provided as a mandatory
    project deliverable during project implementation.}

    \item \emph{Strategy for the management of intellectual property, foreseen
    protection measures}: if relevant, discuss the strategy for the management
    of intellectual property, foreseen protection measures, such as patents,
    design rights, copyright, trade secrets, etc., and how these would be used
    to support exploitation.

    \item All measures should be proportionate to the scale of the project, and
    should contain concrete actions to be implemented both during and after the
    end of the project.
\end{itemize}

\subsection{The magnitude and importance of the project’s contribution to the
expected scientific, societal and economic impacts}

\begin{itemize}
    \item Provide a narrative explaining how the project’s results are expected
    to make a difference in terms of impact, beyond the immediate scope and
    duration of the project. The narrative should include the components below,
    tailored to your project.

    \item Be specific, referring to the effects of your project, and not R\&I
    in general in this field. State the target groups that would benefit.

    \begin{itemize}
        \item \emph{Expected scientific impact(s)}: e.g. contributing to specific
        scientific advances, across and within disciplines, creating new knowledge,
        reinforcing scientific equipment and instruments, computing systems (i.e.
        research infrastructures);

        \item \emph{Expected economic/technological impact(s)}: e.g. bringing new
        products, services, business processes to the market, increasing efficiency,
        decreasing costs, increasing profits, contributing to standards’ setting,
        etc.

        \item \emph{Expected societal impact(s)}: e.g. decreasing CO2 emissions,
        decreasing avoidable mortality, improving policies and decision-making,
        raising consumer awareness.
    \end{itemize}

    \item Only include such outcomes and impacts where your project would make
    a significant and direct contribution. Avoid describing very tenuous links
    to wider impacts.

    \item Give an indication of the magnitude and importance of the project's
    contribution to the expected outcomes and impacts, should the project be
    successful. Provide quantified estimates where possible and meaningful.
    ``Magnitude'' refers to how widespread the outcomes and impacts are likely
    to be. For example, in terms of the size of the target group, or the
    proportion of that group, that should benefit over time; ``Importance''
    refers to the value of those benefits. For example, number of additional
    healthy life years; efficiency savings in energy supply.
\end{itemize}

\section{Quality and Efficiency of the Implementation}

\subsection{Quality and effectiveness of the work plan, assessment of risks and
appropriateness of the effort assigned to work packages}

At a minimum, address the following aspects:

\begin{itemize}
    \item Brief presentation of the overall structure of the work plan,
    including deliverables and milestones.

    \item Timing of the different work packages and their components;

    \item Mechanisms in place to assess and mitigate risks (of research and/or
    administrative nature).
\end{itemize}

A Gantt chart must be included and should indicate the proposed Work Packages
(WP), major deliverables, milestones, secondments, placements. This Gantt chart
counts towards the 10-page limit. The schedule in the Gantt chart should indicate
the number of months elapsed from the start of the action (Month 1).

\subsection{Quality and capacity of the host institutions and participating
organisations, including hosting arrangements}

At a minimum, address the following aspects:

\begin{itemize}
    \item Hosting arrangements, including integration in the team/institution
    and support services available to the researcher.

    \item Quality and capacity of the participating organisations, including
    infrastructure, logistics and facilities should be outlined in Part B-2
    Section 5 (``Capacity of the Participating Organisations'').
\end{itemize}

Note that for GF, both the quality and capacity of the outgoing Third Country
host and the return host should be outlined.

\subsection*{Associated partners linked to a beneficiary\footnotemark{}}

If applicable, outline here the involvement of any 'associated partners linked
to a beneficiary' (in particular, the name of the entity, the type of link with
the beneficiary and the tasks to be carried out).

\footnotetext{See the definitions section of the MSCA Work Programme for
further information.}

\end{document}

### 2022-08-08 msca-pf-part-b2.tex
add template for part b2

\documentclass[11pt,draftproposal]{msca-pf-2022}
% {{{ packages

% math
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{mathrsfs}
\usepackage{cases}

% pretty links
\usepackage{xparse}
\usepackage[hypertexnames=false,breaklinks=true]{hyperref}
\usepackage[nameinlink, noabbrev]{cleveref}
\usepackage[round]{natbib}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    citecolor=black,
    linkcolor=black
}

% better environments
\usepackage[shortlabels]{enumitem}
% \usepackage{booktabs}
\usepackage{caption}
\usepackage{subcaption}

% better typography
\usepackage[activate={true,nocompatibility}, % activate protrusion and font expansion
            final,              % enable microtype, use draft to disable
            tracking=true,
            kerning=true,       % optimise interactions between characters
            spacing=true,       % more uniform spacing between words
            factor=1100,        % more protrusion
            stretch=10,         % smaller values (default 20, 20) to avoid blurring
            shrink=10]{microtype}
\SetTracking{encoding={*}, shape=sc}{40}

% }}}

% {{{ formatting

% caption format
% NOTE: set format=plain to remove caption indentation
\captionsetup{
    format=hang
}

% }}}

% {{{ title

\title{Part B-2}
\author{}
\date{}

% }}}

\begin{document}

\maketitle

\section{CV of the researcher (indicative length: 5 pages)}

Any information provided in Parts A and B of the proposal should be fully consistent.
Always mention full dates (using format: dd/mm/yyyy). The CV should include the
standard academic and research record. Any research career gaps and/or unconventional
paths should be clearly explained.

At a minimum, the CV should contain:

\begin{enumerate}[a)]
    \item The name of the researcher;
    \item Professional experience (most recent first, with exact dates in format
    dd/mm/yyyy);
    \item Education, including PhD award date (most recent first, with exact
    dates in format: dd/mm/yyyy).
\end{enumerate}

The CV should include information on:

\begin{itemize}
    \item Publications in peer-reviewed scientific journals, peer-reviewed conference
    proceedings,  and/or monographs (they are expected to be open access either
    published or through repositories) and other outputs such as data, software,
    algorithms significant for your research path (they are expected to be open
    access in appropriate repositories to the extent possible; they should be
    accompanied by a very short qualitative assessment of their scientific
    significance and not by the Journal Impact Factor);

    \item Invited presentations to internationally established conferences and/or
    international advanced schools;

    \item Organisation of international conferences, including membership in
    the steering and/or programme committee;

    \item Research expeditions led by the researcher;

    \item Granted patent(s);

    \item Examples of participation in industrial innovation;

    \item Prizes and Awards;

    \item Funding received so far;

    \item Supervising and mentoring activities;

    \item Other items of interest.
\end{itemize}

Applicants who have successfully defended their doctoral thesis before the call
deadline but who have not yet formally been awarded the doctoral degree must
clearly indicate the date of the successful PhD defence (``viva''). Researchers
having their last thesis defence after the call deadline will be automatically
declared ineligible for this call.

\section{Capacity of the Participating Organisation(s)}

Please provide an overview list of all participating organisations (the
beneficiary and, where applicable, all associated partners) using template
table 5.1 below, and more detailed information for each of the participating
organisations (using a separate table for each organisation) using template
table 5.2 below.

Any inter-relationship between the participating organisation(s) or individuals
and other entities/persons appearing (e.g. family ties, shared premises or
facilities, joint ownership, financial interest, overlapping staff or directors,
etc.) must be declared in the proposal.

Applicants should provide additional information regarding the administrative/legal
relations between the department carrying out the work as described in the table
below, and the entity/entities mentioned in Part A of the proposal (i.e. linked
to the given Participant Identification Code – PIC).

Should the proposal be shortlisted for funding, all participating organisations
will have to be registered with the European Commission’s
\href{https://ec.europa.eu/info/funding-tenders/opportunities/portal/screen/how-to-participate/participant-register}{Participant Register Services}. Therefore where
this information is \href{https://ec.europa.eu/info/funding-tenders/opportunities/portal/screen/how-to-participate/participant-register-search}{already known},
please provide in Table 5.1 the (draft or validated) nine digit \emph{Participant
Identification Code} (PIC) for the beneficiary and, where applicable, each
associated partner.

\subsection{Template table: Overview of Participating Organisations}

\begin{msctable}{
    |>{\ra}p{0.15\linewidth}
    |>{\ra}p{0.075\linewidth}
    |>{\ra}p{0.15\linewidth}
    |>{\ra}p{0.15\linewidth}
    |>{\ra}p{0.15\linewidth}
    |>{\ra}p{0.15\linewidth}
    |>{\ra}p{0.15\linewidth}|}
\hline
\rowcolor{gray!40}
\textbf{Organization Role} &
\textbf{PIC} &
\textbf{Legal Entity Short Name} &
\textbf{Academic Orgnization (Y/N)} &
\textbf{Country} &
\textbf{Name of Supervisor} \\
\hline
Beneficiary &
&
&
&
& \\
\hline
Associated partner linked to a beneficiary (if applicable) &
&
&
&
& \\
\hline
Associated partner for outgoing phase (mandatory for GF) &
&
&
&
& \\
\hline
Associated partner for secondment (optional) &
&
&
&
& \\
\hline
Associated partner for non-academic placement (optional) &
&
&
&
& \\
\hline
Other &
&
&
&
& \\
\hline
\end{msctable}

\subsection{Template table: Capacity of the Participating Organisations}

Please complete a separate table for each participating organisation. For the
beneficiary, this table should be maximum 1 page in length; for each associated
partner, the table should be maximum ½ page in length. Choose one of

\begin{itemize}
    \item Beneficiary (compulsory).
    \item Associated partner linked to a beneficiary (if applicable)
    \item Associated partner for outgoing phase (compulsory for GF only)
    \item Associated partner for secondment (optional)
    \item Associated partner for non-academic placement (optional)
\end{itemize}

\begin{msctable}{
    |>{\ra}p{0.5\linewidth}
    |>{\ra}p{0.5\linewidth}|}
\hline
\multicolumn{2}{|l|}{
    \textbf{[Full name + Legal Entity Short Name + Country]}
} \\
\hline
\multicolumn{2}{|l|}{
    \textbf{General description}
} \\
\hline
\textbf{Role and profile of supervisor} & \\
\hline
\textbf{Key research facilities, infrastructure and equipment} &
Demonstrate that the beneficiary has sufficient facilities and infrastructure to host and/or offer a suitable environment for training and transfer of knowledge to the recruited experienced researcher.

If applicable, indicate the name of the associated partner linked to a beneficiary and describe the nature of the link in the corresponding table. \\
\hline
\textbf{Previous and current involvement in EU-funded research and training
programmes/actions/projects} &
Indicate up to 5 relevant EU, national or international research and training
actions/projects in which the institution/department has previously participated
and/or is currently participating. \\
\hline
\end{msctable}

\section{Additional ethics information}

Additional information that could not be included in Part A of the proposal (if needed).

\section{Additional information on security screening}

Additional information on security aspects that could not be included in Part
A of the proposal (if needed).

\section{Letter(s) of commitment from as
    sociated partners (only for hosts of
    outgoing phase of Global Fellowships or non-academic placement)}

Use this section to add scanned copies of the letter(s) of commitment, if applicable.

Minimum requirements:

\begin{itemize}
    \item With heading or stamp from the institution;
    \item Up-to-date document, i.e. not dated prior to the call publication;
    \item Demonstrating the will to actively participate in the (identified) proposal;
    \item Explanation of the precise role.
\end{itemize}

Any additional information the organisation deems useful can be added in the letter.

Note that the expert evaluators will be instructed to disregard the contribution
of any associated partners for which no such evidence of commitment is submitted.

In case the letter fails to provide enough information on the associated partner's
role and/or enough assurance of their commitment in the project (e.g. no signature,
wrong proposal references, outdated letter…), the experts may penalise the
proposal on these aspects under the implementation evaluation criterion.

For GF proposals, and for all proposals requesting a non-academic placement,
\emph{the absence of a letter of commitment will render the proposal inadmissible
and the proposal will not be evaluated}.

\subsection*{Non-binding example of template letter of commitment for PF associated partners}

I undersigned \emph{[title, first name and surname]}, in my quality of
\emph{[role in the organisation]} in \emph{[name of the organisation]} commit
to set up all necessary provisions to participate as associated partner in the
proposal \emph{[proposal number and/or acronym]} submitted to the call
HE-MSCA-PF-2022, should the proposal be funded.

On behalf of \emph{[name of the organisation]}, I also confirm that we will
participate and contribute to the research, innovation and training activities
as planned in this project. In particular, \emph{[name of the organisation]}
will be involved in \emph{[free field for any additional information that the
participating organisation wishes to indicate in order to describe its role and
contribution to the project]}.

I hereby declare that I am entitled to commit into this process the entity I represent.

\hfill \emph{Name, Date, Signature}

\end{document}

### 2022-08-09 msca-pf-part-b2.tex
link tables correctly

@@
 }
+
+% NOTE: this needs to be kept so that the sections match the template!
+\setcounter{section}{3}
 
@@
 beneficiary and, where applicable, all associated partners) using template
-table 5.1 below, and more detailed information for each of the participating
-organisations (using a separate table for each organisation) using template
-table 5.2 below.
+table~\ref{ssc:table1} below, and more detailed information for each of the
+participating organisations (using a separate table for each organisation) using
+template table~\ref{ssc:table2} below.
 
@@
 \subsection{Template table: Overview of Participating Organisations}
+\label{ssc:table1}
 
@@
 \subsection{Template table: Capacity of the Participating Organisations}
+\label{ssc:table2}
 

### 2023-05-02 msca-pf-part-b1-template.tex
rename project to msca-pf
update to 2023 call and v3 of the template

--- 2022-08-08 msca-pf-part-b1.tex
@@
-\documentclass[11pt,draftproposal]{msca-pf-2022}
+\documentclass[11pt,draftproposal]{msca-pf}
 % {{{ packages
@@
 \begin{itemize}
-    \item Describe the quality and pertinence of the R \& I objectives; are the
+    \item Describe the quality and pertinence of the R\&I objectives; are the
     objectives measurable and verifiable? Are they realistically achievable?
@@
         \href{https://ec.europa.eu/info/news/gendered-innovations-2-2020-nov-24_en}{this page}.
+
+        \item If you plan to use, develop and/or deploy artificial intelligence
+        (AI) based systems and/or techniques you must demonstrate their technical
+        robustness. AI-based systems or techniques should be, or be developed to
+        become:
+
+        \begin{itemize}
+            \item technically robust, accurate and reproducible, and able to
+            deal with and inform about possible failures, inaccuracies and
+            errors, proportionate to the assessed risk they pose,
+
+            \item socially robust, in that they duly consider the context and
+            environment in which they operate,
+
+            \item reliable and function as intended, minimizing unintentional
+            and unexpected harm, preventing unacceptable harm and safeguarding
+            the physical and mental integrity of humans,
+
+            \item able to provide a suitable explanation of their decision-making
+            processes, whenever they can have a significant impact on people’s
+            lives.
+        \end{itemize}
     \end{itemize}
@@
 
-    \item \emph{Open science is an approach based on open cooperative work and systematic
+    \emph{Open science is an approach based on open cooperative work and systematic
     sharing of knowledge and tools as early and widely as possible in the process.
@@
 
-    \item \emph{Please note that this does not refer to outreach actions that may be
+    \emph{Please note that this does not refer to outreach actions that may be
     planned as part of the communication, dissemination and exploitation activities.
@@
 
-    \item \emph{For guidance on open science practices and research data management,
+    \emph{For guidance on open science practices and research data management,
     please refer to the relevant section of the \href{https://ec.europa.eu/info/funding-tenders/opportunities/docs/2021-2027/horizon/guidance/programme-guide_horizon_en.pdf}{HE Programme Guide}
     on the Funding \& Tenders Portal.}
+
+    Please also see the “how to evaluate open science in Horizon Europe proposals”
+    video on the \href{https://ec.europa.eu/info/funding-tenders/opportunities/portal/screen/support/videos}{Funding \& Tenders portal}.
 \end{itemize}
@@
 \begin{itemize}
-    \item \emph{Expected} skill development of the researcher.
-    \item \emph{Expected} impact of the proposed research and training activities on
-    the researcher's career perspectives inside and/or outside academia.
+    \item Specific measures to enhance career perspectives and employability of
+    the researcher inside and/or outside academia.
+    \item \emph{Expected} contribution of proposed skills development to the
+    future career of the researcher.
 \end{itemize}
@@
     in general in this field. State the target groups that would benefit.
-
+Partial alignment of text with standard application form template for criteria 2.3
     \begin{itemize}
@@
     successful. Provide quantified estimates where possible and meaningful.
+
     ``Magnitude'' refers to how widespread the outcomes and impacts are likely
     to be. For example, in terms of the size of the target group, or the
-    proportion of that group, that should benefit over time; ``Importance''
-    refers to the value of those benefits. For example, number of additional
-    healthy life years; efficiency savings in energy supply.
+    proportion of that group, that should benefit over time.
+
+    ``Importance'' refers to the value of those benefits. For example, number of
+    additional healthy life years; efficiency savings in energy supply.
 \end{itemize}

### 2023-05-02 msca-pf-part-b2-template.tex
add msclongtable wrapper
rename project to msca-pf
update to 2023 call and v3 of the template

--- 2022-08-09 msca-pf-part-b2.tex
@@
 \begin{msctable}{
-    |>{\ra}p{0.15\linewidth}
+    |>{\ra}p{0.165\linewidth}
     |>{\ra}p{0.075\linewidth}
     |>{\ra}p{0.15\linewidth}
-    |>{\ra}p{0.15\linewidth}
-    |>{\ra}p{0.15\linewidth}
-    |>{\ra}p{0.15\linewidth}
+    |>{\ra}p{0.155\linewidth}
+    |>{\ra}p{0.155\linewidth}
+    |>{\ra}p{0.155\linewidth}
     |>{\ra}p{0.15\linewidth}|}
@@
 \rowcolor{gray!40}
-\textbf{Organization Role} &
+\textbf{Organisation Role} &
 \textbf{PIC} &
 \textbf{Legal Entity Short Name} &
-\textbf{Academic Orgnization (Y/N)} &
+\textbf{Academic Organisation (Y/N)} &
 \textbf{Country} &
@@
 
-\begin{msctable}{
-    |>{\ra}p{0.5\linewidth}
-    |>{\ra}p{0.5\linewidth}|}
+\begin{msclongtable}[\small]{
+    |>{\ra}p{0.3\linewidth}
+    |>{\ra}p{0.66\linewidth}|}
+\hline
+\multicolumn{2}{|l|}{
+    \textbf{[Role]}
+} \\
 \hline
@@
 \hline
-\end{msctable}
+\end{msclongtable}
 
@@
 
-\section{Letter(s) of commitment from as
-    sociated partners (only for hosts of
-    outgoing phase of Global Fellowships or non-academic placement)}
+\section{Environmental considerations in light of MSCA Green Charter}
+
+Please explain how the proposed project would strive to adhere to the MSCA Green
+Charter\footnotemark{} during its implementation.
+
+\footnotetext{MSCA Green Charter \url{https://ec.europa.eu/msca/green_charter}.
+While the MSCA Green Charter is non-binding and adherence to it will not be
+subject to evaluation, funded projects are strongly encouraged to take into
+account the principles it sets out.}
+
+\section{Required for Global Fellowships only: Letter(s) of commitment from
+    associated partners (hosting of the outgoing phase)}
 
@@
 
-For GF proposals, and for all proposals requesting a non-academic placement,
-\emph{the absence of a letter of commitment will render the proposal inadmissible
-and the proposal will not be evaluated}.
+For GF proposals \emph{the absence of a letter of commitment will render the
+proposal inadmissible and the proposal will not be evaluated}.
 
@@
 proposal \emph{[proposal number and/or acronym]} submitted to the call
-HE-MSCA-PF-2022, should the proposal be funded.
+HE-MSCA-PF-2023, should the proposal be funded.
 

### 2024-05-30 msca-pf-part-b1-template.tex
feat: simplify templates and remove packages

@@
 
-% math
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{stmaryrd}
-\usepackage{mathrsfs}
-\usepackage{cases}
-
-% pretty links
-\usepackage{xparse}
-\usepackage[hypertexnames=false,breaklinks=true]{hyperref}
+% better environments
 \usepackage[nameinlink, noabbrev]{cleveref}
-\usepackage[round]{natbib}
-\hypersetup{
-    colorlinks=true,
-    urlcolor=blue,
-    citecolor=black,
-    linkcolor=black
-}
-
-% better environments
 \usepackage[shortlabels]{enumitem}
@@
             tracking=true,
-            kerning=true,       % optimise interactions between characters
-            spacing=true,       % more uniform spacing between words
             factor=1100,        % more protrusion
@@
 
-% caption format
-% NOTE: set format=plain to remove caption indentation
-\captionsetup{
-    format=hang
-}
+% NOTE: this needs to be kept so that the sections match the template!
+\setcounter{section}{1}
 
@@
 
-\subsection*{Associated partners linked to a beneficiary\footnotemark{}}
+\subsection*{Associated partners linked to a beneficiary {\protect\footnotemark{}}}
 

### 2024-05-30 msca-pf-part-b2-template.tex
feat: simplify templates and remove packages

@@
 
-% math
-\usepackage{amsmath}
-\usepackage{amsthm}
-\usepackage{stmaryrd}
-\usepackage{mathrsfs}
-\usepackage{cases}
-
-% pretty links
-\usepackage{xparse}
-\usepackage[hypertexnames=false,breaklinks=true]{hyperref}
+% better environments
 \usepackage[nameinlink, noabbrev]{cleveref}
-\usepackage[round]{natbib}
-\hypersetup{
-    colorlinks=true,
-    urlcolor=blue,
-    citecolor=black,
-    linkcolor=black
-}
-
-% better environments
 \usepackage[shortlabels]{enumitem}
-% \usepackage{booktabs}
+\usepackage{booktabs}
 \usepackage{caption}
@@
 % {{{ formatting
-
-% caption format
-% NOTE: set format=plain to remove caption indentation
-\captionsetup{
-    format=hang
-}
 

### 2024-05-30 msca-pf-part-b1-template.tex
feat: update templates for 2024 call

@@
 % NOTE: this needs to be kept so that the sections match the template!
-\setcounter{section}{1}
+\setcounter{section}{0}
 
@@
 \section{Excellence}
+\label{REL-EVA-RE}
 
-\subsection{Quality and pertinence of the project's research and innovation objectives}
+\subsection{
+    Quality and pertinence of the project's research and innovation objectives
+    (and the extent to which they are ambitious, and go beyond the state of the art)}
 
@@
 
-\subsection{Soundness of the proposed methodology}
+\subsection{
+    Soundness of the proposed methodology
+    (including interdisciplinary approaches, consideration of the gender
+    dimension and other diversity aspects if relevant for the research project,
+    and the quality of open science practices)}
 
@@
     \begin{itemize}
-        \item Remember that that this question relates to the content of the
+        \item Remember that that this question relates to the \emph{content} of the
         planned research and innovation activities, and not to gender balance
@@
     Please also see the “how to evaluate open science in Horizon Europe proposals”
-    video on the \href{https://ec.europa.eu/info/funding-tenders/opportunities/portal/screen/support/videos}{Funding \& Tenders portal}.
+    video on the \href{https://ec.europa.eu/info/funding-tenders/opportunities/portal/screen/support/videos}{Funding \& Tenders portal} and
+    \href{https://rea.ec.europa.eu/open-science_en}{Open Science - European Commission (europa.eu)}.
 \end{itemize}
@@
 
-    \item Rationale and added-value of the non-academic placement (if applicable).
+    \item Rationale and added-value of the non-academic placement (if applicable)
+    and secondment (if applicable).
 \end{itemize}
@@
 \section{Impact}
+\label{IMP-ACT-IA}
 
@@
 including communication activities}
+\label{COM-DIS-VIS-CDV}
 
@@
     in general in this field. State the target groups that would benefit.
-Partial alignment of text with standard application form template for criteria 2.3
+
+    \item The impacts of your project may be:
+
     \begin{itemize}
-        \item \emph{Expected scientific impact(s)}: e.g. contributing to specific
-        scientific advances, across and within disciplines, creating new knowledge,
-        reinforcing scientific equipment and instruments, computing systems (i.e.
-        research infrastructures);
+        \item \emph{Scientific}: e.g. contributing to specific scientific advances,
+        across and within disciplines, creating new knowledge, reinforcing
+        scientific equipment and instruments, computing systems (i.e. research
+        infrastructures);
 
-        \item \emph{Expected economic/technological impact(s)}: e.g. bringing new
+        \item \emph{Economic/technological}: e.g. bringing new
         products, services, business processes to the market, increasing efficiency,
@@
 
-        \item \emph{Expected societal impact(s)}: e.g. decreasing CO2 emissions,
+        \item \emph{Societal}: e.g. decreasing CO2 emissions,
         decreasing avoidable mortality, improving policies and decision-making,
@@
     contribution to the expected outcomes and impacts, should the project be
-    successful. Provide quantified estimates where possible and meaningful.
+    successful. Provide credible quantified estimates where possible and meaningful.
 
@@
 \section{Quality and Efficiency of the Implementation}
+\label{WRK-PLA-WP}
 
@@
 A Gantt chart must be included and should indicate the proposed Work Packages
-(WP), major deliverables, milestones, secondments, placements. This Gantt chart
-counts towards the 10-page limit. The schedule in the Gantt chart should indicate
-the number of months elapsed from the start of the action (Month 1).
+(WP), major deliverables, milestones, secondments, placements, if applicable.
+This Gantt chart counts towards the 10-page limit.
+
+The schedule in the Gantt chart should indicate the number of months elapsed
+from the start of the action (Month 1).
 
@@
     \item Quality and capacity of the participating organisations, including
-    infrastructure, logistics and facilities should be outlined in Part B-2
-    Section 5 (``Capacity of the Participating Organisations'').
+    infrastructure, logistics and facilities. Additional information should be
+    outlined in Part B-2 Section 5 (``Capacity of the Participating Organisations'').
 \end{itemize}
@@
 \end{document}
+
+% kate: default-dictionary en_GB;

### 2024-05-30 msca-pf-part-b2-template.tex
feat: update templates for 2024 call

@@
 
-Applicants who have successfully defended their doctoral thesis before the call
+Applicants who have successfully defended their doctoral thesis \emph{before} the call
 deadline but who have not yet formally been awarded the doctoral degree must
@@
 below, and the entity/entities mentioned in Part A of the proposal (i.e. linked
-to the given Participant Identification Code – PIC).
+to the given Participant Identification Code –- PIC).
 
@@
 Please complete a separate table for each participating organisation. For the
-beneficiary, this table should be maximum 1 page in length; for each associated
-partner, the table should be maximum ½ page in length. Choose one of
+beneficiary, this table should be \emph{maximum 1 page in length}; for each associated
+partner, the table should be \emph{maximum ½ page in length}. Choose one of
 
@@
 \textbf{Key research facilities, infrastructure and equipment} &
-Demonstrate that the beneficiary has sufficient facilities and infrastructure to host and/or offer a suitable environment for training and transfer of knowledge to the recruited experienced researcher.
+\emph{Demonstrate that the beneficiary has sufficient facilities and infrastructure
+to host and/or offer a suitable environment for training and transfer of knowledge
+to the recruited experienced researcher.}
 
-If applicable, indicate the name of the associated partner linked to a beneficiary and describe the nature of the link in the corresponding table. \\
+\bigskip
+
+\emph{If applicable, indicate the name of the associated partner linked to a beneficiary
+and describe the nature of the link in the corresponding table.} \\
 \hline
@@
 programmes/actions/projects} &
-Indicate up to 5 relevant EU, national or international research and training
+\emph{Indicate up to 5 relevant EU, national or international research and training
 actions/projects in which the institution/department has previously participated
-and/or is currently participating. \\
+and/or is currently participating.} \\
 \hline
@@
 Please explain how the proposed project would strive to adhere to the MSCA Green
-Charter\footnotemark{} during its implementation.
+Charter\footnotemark{} during its implementation. Please indicate here --
+max 1/2 page -- what actions you propose to take to ensure the sustainable
+implementation of project and to mitigate its environmental impact, in line
+with the principles set out in the MSCA Green Charter.
 
-\footnotetext{MSCA Green Charter \url{https://ec.europa.eu/msca/green_charter}.
-While the MSCA Green Charter is non-binding and adherence to it will not be
-subject to evaluation, funded projects are strongly encouraged to take into
-account the principles it sets out.}
+\footnotetext{MSCA Green Charter \url{https://ec.europa.eu/msca/green_charter}.}
 
-\section{Required for Global Fellowships only: Letter(s) of commitment from
+\section{
+    Required for Global Fellowships only: Letter(s) of commitment from
     associated partners (hosting of the outgoing phase)}
@@
 proposal \emph{[proposal number and/or acronym]} submitted to the call
-HE-MSCA-PF-2023, should the proposal be funded.
+HE-MSCA-2024-PF, should the proposal be funded.
 

### 2024-08-27 msca-pf-part-b1-template.tex
feat: add recommended tags to the template

@@
 
-\section{Excellence}
-\label{REL-EVA-RE}
+\textit{The text in each section is provided only as guidance and should be deleted
+in the final application (including this text). The tags in the section titles
+and at the end of certain sections should be \textbf{kept as is}. They are used for
+automatic document processing and are highly recommended by the programme.}
+
+\textit{When in doubt, always consult the official template and programme guide!}
+
+\section{Excellence \mscatag{REL-EVA-RE}}
 
@@
 
-\section{Impact}
+\section{Impact \mscatag{IMP-ACT-IA}}
 \label{IMP-ACT-IA}
@@
 outcomes and impacts, as set out in the dissemination and exploitation plan,
-including communication activities}
+including communication activities \mscatag{COM-DIS-VIS-CDV}}
 \label{COM-DIS-VIS-CDV}
@@
 
-\section{Quality and Efficiency of the Implementation}
+\mscatagend{COM-DIS-VIS-CDV} \mscatagend{IMP-ACT-IA}
+
+\section{Quality and Efficiency of the Implementation
+         \mscatag{QUA-LIT-QL} \mscatag{WRK-PLA-WP} \mscatag{CON-SOR-CS} \mscatag{PRJ-MGT-PM}}
 \label{WRK-PLA-WP}
@@
 
+\mscatagend{PRJ-MGT-PM} \mscatagend{CON-SOR-CS} \mscatagend{WRK-PLA-WP}
+\mscatagend{QUA-LIT-QL}
 \end{document}

### 2024-08-27 msca-pf-part-b2-template.tex
feat: add recommended tags to the template

@@
 \maketitle
+
+\textit{The text in each section is provided only as guidance and should be deleted
+in the final application (including this text). However, some of the tables
+are part of the document format and should be used and expanded from the ones
+provided here.}
+
+\textit{When in doubt, always consult the official template and programme guide!}
 

### 2024-08-27 msca-pf-part-b2-template.tex
feat: rework helper environments and showcase cv

@@
 
+% {{{ commands
+
+\NewDocumentCommand \ra {} {\raggedright\arraybackslash}
+
+% }}}
+
 % {{{ title
@@
 \date{}
+
+% NOTE: update these as necessary
+% \mscaidentifier{HORIZON-MSCA-2024-PF-01}
+% \mscaproject{TDB}
 
@@
 
+\subsection{Template CV}
+
+This template is only added to showcase the commands used to create the CV. As
+stated above, there is no mandatory format and these commands are mainly added
+as inspiration.
+
+\subsubsection*{Education}
+
+\begin{cvitem}
+\cventry{DD/MM/YYYY DD/MM/YYYY}{Ph.D. in Aerospace Engineering}{University Name}{Location}
+\cvdetail{Title}{Title of my Ph.D}
+\cvdetail{Advisor}{John Doe}
+\end{cvitem}
+
+\subsubsection*{Work Experience}
+
+\begin{cvitem}
+\cventry{DD/MM/YYYY DD/MM/YYYY}{Job Title}{Company / University}{Location}
+\cvdetail{Description}{Job description in short}
+\end{cvitem}
+
+\subsubsection*{Publications}
+
+\begin{cvitem}
+\cvpub{DD/MM/YYYY}{John Doe, Jane Doe}{Title of Paper}{Journal Name, Vol. XX, pp. XX--XX}
+\cvdetail{Description}{Main findings of the paper}
+\cvdetail{URL}{DOI or arXiV URL}
+\end{cvitem}
+
 \section{Capacity of the Participating Organisation(s)}
@@
 
-\begin{msctable}{
-    |>{\ra}p{0.165\linewidth}
-    |>{\ra}p{0.075\linewidth}
-    |>{\ra}p{0.15\linewidth}
-    |>{\ra}p{0.155\linewidth}
-    |>{\ra}p{0.155\linewidth}
-    |>{\ra}p{0.155\linewidth}
-    |>{\ra}p{0.15\linewidth}|}
-\hline
-\rowcolor{gray!40}
-\textbf{Organisation Role} &
-\textbf{PIC} &
-\textbf{Legal Entity Short Name} &
-\textbf{Academic Organisation (Y/N)} &
-\textbf{Country} &
-\textbf{Name of Supervisor} \\
-\hline
+Only relevant rows from the table should be kept.
+
+\begin{mscaorgoverview}
 Beneficiary &
@@
 \hline
-\end{msctable}
+\end{mscaorgoverview}
 
@@
 
-\begin{msclongtable}[\small]{
-    |>{\ra}p{0.3\linewidth}
-    |>{\ra}p{0.66\linewidth}|}
-\hline
+\begin{mscaorgcapacity}
 \multicolumn{2}{|l|}{
@@
 \hline
-\end{msclongtable}
+\end{mscaorgcapacity}
 

### 2024-08-27 msca-pf-part-b2-template.tex
docs: move cv example to README

@@
 declared ineligible for this call.
-
-\subsection{Template CV}
-
-This template is only added to showcase the commands used to create the CV. As
-stated above, there is no mandatory format and these commands are mainly added
-as inspiration.
-
-\subsubsection*{Education}
-
-\begin{cvitem}
-\cventry{DD/MM/YYYY DD/MM/YYYY}{Ph.D. in Aerospace Engineering}{University Name}{Location}
-\cvdetail{Title}{Title of my Ph.D}
-\cvdetail{Advisor}{John Doe}
-\end{cvitem}
-
-\subsubsection*{Work Experience}
-
-\begin{cvitem}
-\cventry{DD/MM/YYYY DD/MM/YYYY}{Job Title}{Company / University}{Location}
-\cvdetail{Description}{Job description in short}
-\end{cvitem}
-
-\subsubsection*{Publications}
-
-\begin{cvitem}
-\cvpub{DD/MM/YYYY}{John Doe, Jane Doe}{Title of Paper}{Journal Name, Vol. XX, pp. XX--XX}
-\cvdetail{Description}{Main findings of the paper}
-\cvdetail{URL}{DOI or arXiV URL}
-\end{cvitem}
 

### 2024-08-27 msca-pf-part-b2-template.tex
feat: add latex labels to each section

@@
 
-\NewDocumentCommand \ra {} {\raggedright\arraybackslash}
+% add your own fancy commands
+% \NewDocumentCommand \mycmd { m } {\textbf{#1}}
 
@@
 \section{CV of the researcher (indicative length: 5 pages)}
+\label{sc:cv}
 
@@
 \section{Capacity of the Participating Organisation(s)}
+\label{sc:organisations}
 
@@
 beneficiary and, where applicable, all associated partners) using template
-table~\ref{ssc:table1} below, and more detailed information for each of the
-participating organisations (using a separate table for each organisation) using
-template table~\ref{ssc:table2} below.
+table~\ref{ssc:organisations:overview} below, and more detailed information for
+each of the participating organisations (using a separate table for each
+organisation) using template table~\ref{ssc:organisations:capacity} below.
 
@@
 \subsection{Template table: Overview of Participating Organisations}
-\label{ssc:table1}
-
+\label{ssc:organisations:overview}
 Only relevant rows from the table should be kept.
@@
 \subsection{Template table: Capacity of the Participating Organisations}
-\label{ssc:table2}
+\label{ssc:organisations:capacity}
 
@@
 \section{Additional ethics information}
+\label{sc:ethics}
 
@@
 \section{Additional information on security screening}
+\label{sc:security}
 
@@
 \section{Environmental considerations in light of MSCA Green Charter}
+\label{sc:environment}
 
@@
     associated partners (hosting of the outgoing phase)}
+\label{sc:commitment_letter}
 

### 2025-04-28 msca-pf-part-b1-template.tex
feat: rework helper environments and showcase cv
feat: add latex labels to each section
feat: bump year to 2025
feat: some more updates from the 4.1 changes

@@
 
+% {{{ commands
+
+% add your own fancy commands
+% \NewDocumentCommand \mycmd { m } {\textbf{#1}}
+
+% }}}
+
 % {{{ title
@@
 \date{}
+
+% NOTE: update these as necessary
+% \mscaidentifier{HORIZON-MSCA-2025-PF-01}
+% \mscaproject{TDB}
 
@@
 \section{Excellence \mscatag{REL-EVA-RE}}
+\label{sc:excellence}
 
-\subsection{
-    Quality and pertinence of the project's research and innovation objectives
+\subsection{Quality and pertinence of the project's research and innovation objectives
     (and the extent to which they are ambitious, and go beyond the state of the art)}
+    \mscatag{QUA-LIT-QL}
+\label{ssc:excellence:quality}
 
@@
 
-\subsection{
-    Soundness of the proposed methodology
+\subsection{Soundness of the proposed methodology
     (including interdisciplinary approaches, consideration of the gender
@@
     and the quality of open science practices)}
+\label{ssc:excellence:methodology}
 
@@
 
-    \footnotetext{Interdisciplinarity means the integration of information, data,
-    techniques, tools, perspectives, concepts or theories from two or more
-    scientific disciplines.}
-
     \item \emph{Gender dimension and other diversity aspects}: Describe how the
@@
         methods of sex / gender analysis and the issues to be taken into account,
-        please refer to
-        \href{https://ec.europa.eu/info/news/gendered-innovations-2-2020-nov-24_en}{this page}.
-
-        \item If you plan to use, develop and/or deploy artificial intelligence
-        (AI) based systems and/or techniques you must demonstrate their technical
-        robustness. AI-based systems or techniques should be, or be developed to
-        become:
-
-        \begin{itemize}
-            \item technically robust, accurate and reproducible, and able to
-            deal with and inform about possible failures, inaccuracies and
-            errors, proportionate to the assessed risk they pose,
-
-            \item socially robust, in that they duly consider the context and
-            environment in which they operate,
-
-            \item reliable and function as intended, minimizing unintentional
-            and unexpected harm, preventing unacceptable harm and safeguarding
-            the physical and mental integrity of humans,
-
-            \item able to provide a suitable explanation of their decision-making
-            processes, whenever they can have a significant impact on people’s
-            lives.
-        \end{itemize}
+        please refer to this
+        \href{https://op.europa.eu/en/publication-detail/-/publication/33b4c99f-2e66-11eb-b27b-01aa75ed71a1/language-en}{link}.
     \end{itemize}
@@
     nature of your work in a way that will increase the chances of the project
-    delivering on its objectives [e.g. up to 1/2 page, including research data
-    management]. If you believe that none of these practices are appropriate for
-    your project, please provide a justification here.
+    delivering on its objectives \emph{[1/2 page]}. If you believe that none of
+    these practices are appropriate for your project, please provide a justification
+    here.
 
@@
 
-    \item \emph{Research data management and management of other research outputs}:
-    Applicants generating/collecting data and/or other research outputs (except for
-    publications) during the project must explain how the data will be managed
-    in line with the FAIR principles (Findable, Accessible, Interoperable,
-    Reusable).
+    \item Proposals selected for funding under Horizon Europe will need to develop
+    a detailed data management plan (DMP) for making their data/research outputs
+    findable, accessible, interoperable and reusable (FAIR) as a deliverable by
+    month 6 and revised towards the end of a project's lifetime. The DMP should
+    describe how research outputs (especially research data) generated and/or
+    collected during the project will be managed so as to ensure that they are
+    findable, accessible, interoperable and reusable.
 
     \emph{For guidance on open science practices and research data management,
-    please refer to the relevant section of the \href{https://ec.europa.eu/info/funding-tenders/opportunities/docs/2021-2027/horizon/guidance/programme-guide_horizon_en.pdf}{HE Programme Guide}
+    please refer to the relevant section of the
+    \href{https://ec.europa.eu/info/funding-tenders/opportunities/docs/2021-2027/horizon/temp-form/af/af_he-msca-pf_en.pdf}{HE Programme Guide}
     on the Funding \& Tenders Portal.}
-
-    Please also see the “how to evaluate open science in Horizon Europe proposals”
-    video on the \href{https://ec.europa.eu/info/funding-tenders/opportunities/portal/screen/support/videos}{Funding \& Tenders portal} and
-    \href{https://rea.ec.europa.eu/open-science_en}{Open Science - European Commission (europa.eu)}.
 \end{itemize}
@@
     knowledge between the researcher and the host}
+\label{ssc:excellence:supervision}
 
@@
 encouraged to follow the recommendations outlined in the
-\href{https://data.europa.eu/doi/10.2766/508311}{MSCA Guidelines on Supervision}\footnotemark{}.
-
-\footnotetext{While the MSCA Guidelines on Supervision are non-binding,
-funded-projects are strongly encouraged to take them into account.}
+\href{https://data.europa.eu/doi/10.2766/508311}{MSCA Guidelines on Supervision}.
 
@@
     experience, competences and skills}
+\label{ssc:excellence:researcher}
 
@@
 \section{Impact \mscatag{IMP-ACT-IA}}
-\label{IMP-ACT-IA}
+\label{sc:impact}
 
@@
     development}
+\label{ssc:impact:career}
 
@@
     including communication activities \mscatag{COM-DIS-VIS-CDV}}
-\label{COM-DIS-VIS-CDV}
+\label{ssc:impact:outcomes}
 
@@
     expected scientific, societal and economic impacts}
+\label{ssc:impact:future}
 
@@
          \mscatag{QUA-LIT-QL} \mscatag{WRK-PLA-WP} \mscatag{CON-SOR-CS} \mscatag{PRJ-MGT-PM}}
-\label{WRK-PLA-WP}
+\label{sc:implementation}
 
@@
     appropriateness of the effort assigned to work packages}
+\label{ssc:implementation:workplan}
 
@@
 The schedule in the Gantt chart should indicate the number of months elapsed
-from the start of the action (Month 1).
+from the start of the action (Month 1, Month 2, etc.) but no actual dates.
 
@@
 organisations, including hosting arrangements}
+\label{ssc:implementation:host}
 
@@
 \begin{itemize}
-    \item Hosting arrangements, including integration in the team/institution
+    \item Hosting arrangements, including integration in the team/institution(s)
     and support services available to the researcher.
@@
 \subsection*{Associated partners linked to a beneficiary {\protect\footnotemark{}}}
+\label{ssc:implementation:partners}
 

### 2025-05-10 msca-pf-part-b1-template.tex
feat: make font 12pt like template and update tags

@@
-\documentclass[11pt,draftproposal]{msca-pf}
+\documentclass[12pt,draftproposal]{msca-pf}
 % {{{ packages
@@
     (and the extent to which they are ambitious, and go beyond the state of the art)}
-    \mscatag{QUA-LIT-QL}
 \label{ssc:excellence:quality}
@@
 The schedule in the Gantt chart should indicate the number of months elapsed
-from the start of the action (Month 1, Month 2, etc.) but no actual dates.
+from the start of the action (Month 1, Month 2, etc.), but no actual dates.
 
@@
 
-\mscatagend{PRJ-MGT-PM} \mscatagend{CON-SOR-CS} \mscatagend{WRK-PLA-WP}
-\mscatagend{QUA-LIT-QL}
+\mscatagend{CON-SOR-CS} \mscatagend{PRJ-MGT-PM} \mscatagend{QUA-LIT-QL} \mscatagend{WRK-PLA-WP}
 \end{document}

### 2025-05-10 msca-pf-part-b1-template.tex
feat: update text according to template

@@
 
+    \footnotetext{\emph{Interdisciplinarity} means the integration of information,
+    data, techniques, tools, perspectives, concepts or theories from two or
+    more scientific disciplines.}
+
     \item \emph{Gender dimension and other diversity aspects}: Describe how the
@@
 
-Employers and/or founders should ensure that a person is clearly identified to
+Employers and/or funders should ensure that a person is clearly identified to
 whom researchers can refer for the performance of their professional duties, and
@@
 encouraged to follow the recommendations outlined in the
-\href{https://data.europa.eu/doi/10.2766/508311}{MSCA Guidelines on Supervision}.
+\href{https://data.europa.eu/doi/10.2766/508311}{MSCA Guidelines on Supervision}
+\footnotemark{}.
+
+\footnotetext{While the MSCA Guidelines on Supervision are non-binding,
+funded-projects are strongly encouraged to take them into account.}
 

### 2025-05-10 msca-pf-part-b2-template.tex
feat: bump year to 2025
feat: make font 12pt like template and update tags
feat: update text according to template

@@
 % NOTE: update these as necessary
-% \mscaidentifier{HORIZON-MSCA-2024-PF-01}
+% \mscaidentifier{HORIZON-MSCA-2025-PF-01}
 % \mscaproject{TDB}
@@
 Any information provided in Parts A and B of the proposal should be fully consistent.
-Always mention full dates (using format: dd/mm/yyyy). The CV should include the
-standard academic and research record. Any research career gaps and/or unconventional
-paths should be clearly explained.
+Always mention full consecutive dates (using format: dd/mm/yyyy). The CV should
+include the standard academic and research record. Any research career gaps
+and/or unconventional paths should be clearly explained and the dates must match
+the ones provided in Part A (if applicable).
 
@@
 \label{ssc:organisations:overview}
+
 Only relevant rows from the table should be kept.
@@
 \hline
-Associated partner for secondment (optional) &
+Associated partner for secondment (if applicable) &
 &
@@
 \hline
-Associated partner for non-academic placement (optional) &
-&
-&
-&
-& \\
-\hline
-Other &
+Associated partner for non-academic placement (if applicable) &
 &
@@
     \item Associated partner for outgoing phase (compulsory for GF only)
-    \item Associated partner for secondment (optional)
-    \item Associated partner for non-academic placement (optional)
+    \item Associated partner for secondment (if applicable)
+    \item Associated partner for non-academic placement (if applicable)
 \end{itemize}
@@
 
-Note that the expert evaluators will be instructed to disregard the contribution
-of any associated partners for which no such evidence of commitment is submitted.
-
 In case the letter fails to provide enough information on the associated partner's
@@
 proposal \emph{[proposal number and/or acronym]} submitted to the call
-HE-MSCA-2024-PF, should the proposal be funded.
+HE-MSCA-2025-PF, should the proposal be funded.
 
@@
 will be involved in \emph{[free field for any additional information that the
-participating organisation wishes to indicate in order to describe its role and
-contribution to the project]}.
+participating organisation wishes to indicate in order to describe its role
+and contribution to the project]}.
 

### 2025-09-07 msca-pf-part-b1-template.tex
feat: remove microtype options

@@
 % better typography
-\usepackage[activate={true,nocompatibility}, % activate protrusion and font expansion
-            final,              % enable microtype, use draft to disable
-            tracking=true,
-            factor=1100,        % more protrusion
-            stretch=10,         % smaller values (default 20, 20) to avoid blurring
-            shrink=10]{microtype}
+\usepackage[activate={true,nocompatibility}, tracking=true]{microtype}
 \SetTracking{encoding={*}, shape=sc}{40}

### 2025-09-07 msca-pf-part-b2-template.tex
fix: use 12pt fonts in part-b2 as well
feat: sync microtype setup

@@
 % better typography
-\usepackage[activate={true,nocompatibility}, % activate protrusion and font expansion
-            final,              % enable microtype, use draft to disable
-            tracking=true,
-            factor=1100,        % more protrusion
-            stretch=10,         % smaller values (default 20, 20) to avoid blurring
-            shrink=10]{microtype}
-\SetTracking{encoding={*}, shape=sc}{40}
+\usepackage[activate={true,nocompatibility}, tracking=true]{microtype}
 

### 2025-09-08 msca-pf-part-b2-template.tex
feat: move cv example commands to template

@@
 \end{itemize}
+
+You may modify the template below as necessary to include all relevant information.
+
+\subsubsection*{Education}
+\label{ssc:cv:education}
+
+\begin{cvitem}
+\cventry{DD/MM/YYYY DD/MM/YYYY}{Ph.D. in Aerospace Engineering}{University Name}{Location}
+\cvdetail{Title}{Title of my Ph.D}
+\cvdetail{Advisor}{John Doe}
+\end{cvitem}
+
+\subsubsection*{Positions}
+
+\begin{cvitem}
+\cventry{DD/MM/YYYY DD/MM/YYYY}{Job Title}{Company / University}{Location}
+\cvdetail{Description}{Job description in short}
+\end{cvitem}
+
+% example of a bare entry (same as above without the details)
+\cventryitem{DD/MM/YYYY DD/MM/YYYY}{Job Title}{Company / University}{Location}
+
+\subsubsection*{Publications}
+
+\begin{cvitem}
+\cvpub{DD/MM/YYYY}{John Doe, Jane Doe}{Title of the Paper}
+                  {Journal Name, Vol. XX, pp. XX--XX}
+\cvdetail{Description}{Main findings of the paper}
+\cvdetail{URL}{DOI or arXiV URL}
+\end{cvitem}
+
+% example for a bare publication (same as above without the details)
+\cvpubitem{DD/MM/YYYY}{John Doe, Jane Doe}{Title of the Paper}
+                      {Journal Name, Vo. XX, pp. XX--XX}
 
